IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-05-09 paper/concrete.tex
Fix notation issues with fresh.

  \begin{mathpar}
    \inferrule[C-sandbox]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |iS' = bracket iS (mapsto id' nil)|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh (id')|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |canFlowTo2 il il'|\\
      |iS(id') = Q|\\
      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

>>>>

  \begin{mathpar}
    \inferrule[C-sandbox]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |iS' = bracket iS (mapsto id' nil)|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh id'|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (sandbox ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \mathcal{AV}(|ie|) = \emptyset{}\\
      |canFlowTo2 il il'|\\
      |iS(id') = Q|\\
      |iS' = bracket iS (mapsto id' (il', id,  iv) , Q)|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' iv)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

### 2014-05-09 paper/retrofit.tex
Fix notation issues with fresh.

\and
\inferrule[T-ref]
{ | ap fresh ta | }
{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

@@

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
niconf iS id il (setLabel il')
->
niconf iS id il' unit
|}
%{|fresh (id')|}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = bracket iS (mapsto id' nil)|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' ie|\\
|ap fresh id'|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched box (it1, ldots, itnew)
|}

>>>>

\and
\inferrule[T-ref]
{ | fresh ta | }
{| conf tS (ref tv) -> conf (bracket tS (mapsto ta tv)) ta |}

@@

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
niconf iS id il (setLabel il')
->
niconf iS id il' unit
|}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = bracket iS (mapsto id' nil)|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' ie|\\
|fresh id'|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched box (it1, ldots, itnew)
|}
